---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

In this tutorial, we demonstrate the key functionality of the `RaCE.NMA` package on a hypothetical dataset of results from a network meta-analysis (NMA). The tutorial includes code for model estimation and visualization of results. We begin by loading necessary packages.

```{r warning=FALSE,message=FALSE}
library(RaCE.NMA)
library(reshape2) # data reformatting
library(ggplot2)  # creating nice figures
```

## Exploratory Data Analysis

```{r}
mu_hat <- c(-1, 0, 1, 0)
sigma_hat <- c(0.1, 0.1, 0.1, 1)


data <- t(matrix(rnorm(10000,mean=mu_hat,sd=sigma_hat),nrow=4))
ggplot(as.data.frame(melt(data)),aes(x=factor(Var2),y=value))+
  geom_violin()+theme_bw()+theme(panel.grid.minor = element_blank(),panel.grid.major.x = element_blank())+
  labs(x="Treatment",y="Posterior Relative Intervention Effect")
```




## Estimation

Now, let's fit the RaCE model to our data.

```{r}

```


First, we ensure the chains have converged by assessing trace plots of $K$ and $\mu_j$.

```{r}

```

## Inference



```{r}



```

